Discrete Probability for Discrete Quantum Computing

### 2016-04-30 prob.tex
Briefly read through and fix some typos...

\begin{example}[Dempster-Shafer Theory of Evidence] We have five
  employees whose precise age is not known. All is give is a range for
  each employee:
\[\begin{array}{rcl}
\textrm{Age}(M_1) &=& [22,26] \\
\textrm{Age}(M_2) &=& [20,22] \\
\textrm{Age}(M_3) &=& [30,35] \\
\textrm{Age}(M_4) &=& [20,22] \\
\textrm{Age}(M_5) &=& [28,30] 
\end{array}\]
What is the probability that an employee's age is in the range
$[20,25]$. Looking at the data, it is \emph{possible} for $M_1$'s age
to be within the range, it is \emph{not possible} for $M_3$'s age to
be within the range, and it is \emph{certain} or \emph{necessary} that
$M_4$'s age is in the range. Clearly saying that an event is
\emph{necessary} is equivalent to saying that its complement is
\emph{not possible}. Aggregating the results for the five employees,
we can calculate that is necessary that 2 employees have their ages
within the range, and it is possible that 3 employees have their ages
within the range. We express this formally as saying that the
probability of the event is $[0.4,0.6]$. Now consider another event
asking whether the ages are some other disjoint range
$[26,40]$. Reasoning in a similar way we calculate that the
probability for this event is $[0.4,0.6]$. Now let's take the two events
together and ask about the possibility of the ages to be in the range
$[20,40]$. Clearly that probability must be $[1,1]$ as every
employee's age is in that range. The way to calculate this probability
from the individual probabilities of the events is as follows: 
\begin{itemize}
\item \amr{can you try to fix this... perhaps it is not consistent
    with the interval-valued formalization but it is really nice if we
    can make it work}
\end{itemize}
\qed\end{example}

@@

Turning things around, the strength of evidence that contradicts
$E$ is evidence supporting the complement of $E$

The complement of $E$ must therefore have probability
$\left[1-b,1-a\right]$ which we abbreviate $1-\left[a,b\right]$:

>>>>

\begin{example}[Dempster-Shafer Theory of Evidence] We have five
  employees whose precise age is not known. All is given is a range for
  each employee:
\[\begin{array}{rcl}
\textrm{Age}(M_1) &=& [22,26] \\
\textrm{Age}(M_2) &=& [20,22] \\
\textrm{Age}(M_3) &=& [30,35] \\
\textrm{Age}(M_4) &=& [20,22] \\
\textrm{Age}(M_5) &=& [28,30] 
\end{array}\]
What is the probability that an employee's age is in the range
$[20,25]$? Looking at the data, it is \emph{possible} for $M_1$'s age
to be within the range, it is \emph{not possible} for $M_3$'s age to
be within the range, and it is \emph{certain} or \emph{necessary} that
$M_4$'s age is in the range. Clearly saying that an event is
\emph{necessary} is equivalent to saying that its complement is
\emph{not possible}. Aggregating the results for the five employees,
we can calculate that is necessary that 2 employees have their ages
within the range, and it is possible that 3 employees have their ages
within the range. We express this formally as saying that the
probability of the event is $[0.4,0.6]$. Now consider another event
asking whether the ages are some other disjoint range
$(25,40]$. Reasoning in a similar way we calculate that the
probability for this event is $[0.4,0.6]$. Now let's take the two events
together and ask about the possibility of the ages to be in the range
$[20,40]$. Clearly that probability must be $[1,1]$ as every
employee's age is in that range. The way to calculate this probability
from the individual probabilities of the events is as follows: 
\begin{itemize}
\item \amr{can you try to fix this... perhaps it is not consistent
    with the interval-valued formalization but it is really nice if we
    can make it work}
\end{itemize}
\qed\end{example}

@@

\yutsung{Do we use the law of excluded middle here? You remind me Agda : ) Did
Homotopy Type Theory people said anything about the probability?}

Turning things around, the strength of evidence that contradicts
$E$ is evidence supporting the complement of $E$. The complement of $E$ must
therefore have probability $\left[1-b,1-a\right]$ which we abbreviate $1-\left[a,b\right]$:
